A molecular dynamics study of the solvation of \ce{CO_2}, water, and some organic compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}

### 2018-08-06 ionic_liquids.tex
conclusion revision

\subfloat[]{%
  \includegraphics[width=\linewidth]{ludwigall.pdf}%
}
\caption{Spatial distribution functions (SDFs) of (a) \ce{[B(CN)_4]^-} (green) and \ce{[emim]^+} (yellow) at the isosurface values of 0.138 and 0.12, respectively; and of (b) \ce{[NTf_2]^-} (blue) and \ce{[emim]^+} (white) at the isosurface values of 0.086 and 0.063, respectively.
Fig. (c) corresponds to the SDFs of the anions, only.}
\label{fig:sdf_ions}
\end{figure}

@@

\begin{table*}
\centering
\begin{adjustbox}{width=1\textwidth}
\begin{threeparttable}
\caption{Infinite-dilution activity coefficients in \ce{[emim][B(CN)_4]} at $T = 298.15~/text{K}$ of the pure solutes benzene, hexane, cyclohexane, ethanol, and water.}
\begin{tabular}{c c c c c c  >{\columncolor[gray]{0.8}} c}  
\toprule
Solute & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$  & $\gamma^{\,\infty,\text{sim}}$ & $\gamma^{\, \infty,\text{exp}}$ & $\gamma^{\, \infty,\text{exp}}$  \\
 & (kcal/mol) & (kcal/mol) &  (kcal/mol)  &  & (298.15 K) \cite{Doma_ska_2011} & (303 K) \cite{Yan_2010} \\
\midrule % inserts single-line
hexane OPLS-AA & -2.13 $\pm$ 0.04 & -0.152 $\pm$ 0.007 & -2.282 $\pm$ 0.04 & 6.2 $\pm$ 0.5 & 33.8 & 20.97  \\
cyclohexane& -2.75 $\pm$ 0.06 & - & -2.75 $\pm$ 0.06 & 9 $\pm$ 1 & 16.7 & 13.82 \\
benzene OPLS-AA  & -2.23 $\pm$ 0.05 & -1.29 $\pm$ 0.04 & -3.52 $\pm$ 0.06 & 1.2 $\pm$ 0.1 & 1.13 & 1.31 \\ 
ethanol TRAPPE-UA& -0.73 $\pm$ 0.02 & -4.10 $\pm$ 0.04 & -4.83 $\pm$ 0.04 & 0.41 $\pm$ 0.03 & 1.58 & 1.64  \\
water TIP4P/2005& 1.38 $\pm$ 0.008 & -6.32 $\pm$ 0.03 & -4.94 $\pm$ 0.03 & 2 $\pm$ 1 & 2.65 & 2.24 \\
 \bottomrule
\label{table:gamma} 
\end{tabular}
\end{threeparttable}
\end{adjustbox}
\end{table*}

Since concentrated solutions are the more likely scenario in \ce{CO_2} capture processes, we carried out simulations at the thermodynamic conditions specified in Table \ref{table:solv}, which correspond to close values of \ce{CO_2} molality in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N].

In Fig. we present the results of each iteration according to the scheme proposed in Sec. \ref{sec:partial_pressure}. The predicted values of pressure ($P_s$) reproduce what is observed experimentaly, in the sense that $P_s$ for the system \ce{CO_2}-\ce{[emim][B(CN)_4]} is considerably smaller than the value obtained for \ce{CO_2}-[emim][Tf\textsubscript{2}N].

\begin{figure}[ht]
\includegraphics[width=\linewidth]{pressure_est.pdf}
\caption{$\Delta G_{\lambda_{\,\text{vdW}}}$ profiles corresponding to the insertion of a \ce{CO_2} molecule in \ce{[emim][B(CN)_4]}, which was modeled according to the force fields of (circles) Koller \textit{et al.} \cite{Koller_2012}, (squares) Batista \textit{et al.} \cite{Batista_2015}, (up triangles) Liu \textit{et al.} \cite{Liu_2014}, and (x) Weber y Kirchner \cite{Weber_2016}.}
\label{fig:pressure}
\end{figure}

\section{Concluding remarks}
\label{sec:conclusion}

@@

\end{document}
%rigid treatment of the imidazolium ring \cite{Kobrak_2004,Lynden_Bell_2006}\cite{Rey_Castro_2007}

%\begin{equation}
%\begin{split}
%\Delta G_{\text{sim}} - k_b T \ln \left( \frac{V^{\ast}}{V_1} \right) &= k_b T \ln \left(\frac{P_s}{x_s} \frac{1}{\tilde{\rho}_{\scaleto{LI}{4pt}}} \right) \\
%&= k_b T \ln \left( \frac{K_s}{\tilde{\rho}_{\scaleto{LI}{4pt}} R T} \right),
%\end{split}
%\end{equation}

>>>>

\subfloat[]{%
  \includegraphics[width=\linewidth]{ludwigall.pdf}%
}

\subfloat[]{%
  \includegraphics[width=\linewidth]{anionanion.pdf}%
}
\caption{Spatial distribution functions (SDFs) of (a) \ce{[B(CN)_4]^-} (green) and \ce{[emim]^+} (yellow) at the isosurface values of 0.138 and 0.12, respectively; and of (b) \ce{[NTf_2]^-} (blue) and \ce{[emim]^+} (white) at the isosurface values of 0.086 and 0.063, respectively.
Fig. (c) corresponds to the SDFs of the anions plotted together.}
\label{fig:sdf_ions}
\end{figure}

Since concentrated solutions are the more likely scenario in \ce{CO_2} capture processes, we carried out simulations at the thermodynamic conditions specified in Table \ref{table:solv}, which correspond to close values of \ce{CO_2} molality in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N].
The differences in the \ce{CO_2} molar fractions in this case exemplifies the observation made by Carvalho \textit{et al.} \cite{Carvalho_2016}, mentioned at the introduction of this paper.

In Fig.~\ref{fig:pressure} we show for each system our predictions of the gas-phase pressure ($P_s$), as described in Sec.~\ref{sec:partial_pressure}.
The dotted lines are the experimental pressures, which correspond to the specified values ($P$) in the liquid-phase simulation.
Note that our results reproduce what is experimentally observed, in the sense that the calculated $P_s$ is considerably lower for \ce{CO_2}-\ce{[emim][B(CN)_4]}.
In addition, we see that for  this system the correction to the ideal gas assumption is almost negligible, as $P_s$ is very close to the fugacity ($f^g_s$).
The solvation free energies obtained for \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-[emim][Tf\textsubscript{2}N] were -0.755 $\pm$ 0.01 kcal/mol and -0.542 $\pm$ 0.005, respectively. However, since we employed a different molecule number of \ce{CO_2}, we cannot draw any conclusion regarding the presence of strong interactions with \ce{[emim][B(CN)_4]} that could explain the higher solubility.

\begin{figure}[ht]
\includegraphics[width=\linewidth]{pressure_est.pdf}
\caption{ \ce{CO_2} \ce{[emim][B(CN)_4]} Koller \textit{et al.} \cite{Koller_2012}, (squares)}
\label{fig:pressure}
\end{figure}

@@

\begin{table*}
\centering
\begin{adjustbox}{width=1\textwidth}
\begin{threeparttable}
\caption{Infinite-dilution activity coefficients in \ce{[emim][B(CN)_4]} at $T = 298.15~/text{K}$ of the pure solutes benzene, hexane, cyclohexane, ethanol, and water.}
\begin{tabular}{c c c c c c  >{\columncolor[gray]{0.8}} c}  
\toprule
Solute & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$  & $\gamma^{\,\infty,\text{sim}}$ & $\gamma^{\, \infty,\text{exp}}$ & $\gamma^{\, \infty,\text{exp}}$  \\
 & (kcal/mol) & (kcal/mol) &  (kcal/mol)  &  & (298.15 K) \cite{Doma_ska_2011} & (303 K) \cite{Yan_2010} \\
\midrule % inserts single-line
hexane OPLS-AA & -2.13 $\pm$ 0.04 & -0.152 $\pm$ 0.007 & -2.282 $\pm$ 0.04 & 6.2 $\pm$ 0.5 & 33.8 & 20.97  \\
cyclohexane& -2.75 $\pm$ 0.06 & - & -2.75 $\pm$ 0.06 & 9 $\pm$ 1 & 16.7 & 13.82 \\
benzene OPLS-AA  & -2.23 $\pm$ 0.05 & -1.29 $\pm$ 0.04 & -3.52 $\pm$ 0.06 & 1.2 $\pm$ 0.1 & 1.13 & 1.31 \\ 
ethanol TRAPPE-UA& -0.73 $\pm$ 0.02 & -4.10 $\pm$ 0.04 & -4.83 $\pm$ 0.04 & 0.41 $\pm$ 0.03 & 1.58 & 1.64  \\
water TIP4P/2005& 1.38 $\pm$ 0.008 & -6.32 $\pm$ 0.03 & -4.94 $\pm$ 0.03 & 2 $\pm$ 1 & 2.65 & 2.24 \\
 \bottomrule
\label{table:gamma} 
\end{tabular}
\end{threeparttable}
\end{adjustbox}
\end{table*}
\section{Concluding remarks}
\label{sec:conclusion}

One of the goals of this paper was to compare various available models of \ce{[emim][B(CN)_4]} in terms of their capability to reproduce the experimental Henry constant of \ce{CO_2}.
We have found that only the force field developed by Koller \textit{et al.} \cite{Koller_2012} is able to perform such task, with a small relative error of 2.8 \%.
A key factor for its success seems to be the reparametrization of the LJ parameters for the boron atom carried out in that work, which also allows to accurately reproduce the experimental density of the pure substance.

We focused also on exploring alternative simulation strategies with the goal of gaining computational efficiency.
Particularly, for both \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}, we concluded that the DSF method with $\alpha$ = 0.2 {\AA}$^{-1}$ is a suitable strategy.
Other improvement was the use of rigid bodies to simulate \ce{[emim][B(CN)_4]}.
This required preliminary simulations in order to examine the flexibility of the ethyl chain in \ce{[emim]^+} and the analysis was greatly facilitated by employing useful visualization tools.
It should be remarked that the different models presented a different behavior, as well; reflecting ?

The solvation free energy results at infinite-dilution condition suggest a slightly more favorable solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in  \ce{[emim][NTf_2]}.
However, this picture completely changes at high concentrations: the simulations correctly predicted a considerable lower pressure to dissolve a certain mass of \ce{CO_2} in \ce{[emim][B(CN)_4]}.

Finally, we employed the model of Koller \textit{et al.} \cite{Koller_2012} to predict infinite-dilution activity coefficient of various solutes.
In this case, the results were not satisfactory given the high errors associated to the free energy calculations of the pure solutes, making necessary a revision of the force fields for the solutes in a future work.

@@

\end{document}
